The CMS Data Aggregation System

### 2010-05-04 doc/paper.tex
Bug fix
git-svn-id: svn+ssh://svn.cern.ch/reps/CMSDMWM/DAS/trunk@649 4525493e-7705-40b1-a816-d608a930855b

The individual tests of DAS components (DBS and PhEDEx) shown roughly 
the same performance. Although the time of PhEDEx component was bigger 
due to longer retrieval and parsing time.
The time of PhEDEx component shown in Table \ref{DAS_benchmark} divided 
among: retrieval + parsing step, $\sim$110 sec, and merging step, $\sim$50 sec.
As shown in Table \ref{DAS_benchmark},
the time spent to access individual components (last column) was quite
reasonable, roughly 1 second for both systems. While final time to
get DAS records on disk was about 45 seconds. This was mostly due to I/O and
conversion operations between binary data format used by MongoDB, BSON, to DAS
data format, JSON.

>>>>

The individual tests of DAS components (DBS and PhEDEx) shown roughly 
the same performance. Although the time of PhEDEx component was bigger 
due to longer retrieval and parsing time.
The time of PhEDEx component shown in Table \ref{DAS_benchmark} is divided 
among: retrieval + parsing step, $\sim$110 sec, and merging step, $\sim$50 sec.
As shown in Table \ref{DAS_benchmark},
the time spent to access individual components (last column) was quite
reasonable, roughly 1 second for both systems. While final time to
get DAS records on disk was about 45 seconds. This was mostly due to I/O and
conversion operations between binary data format used by MongoDB, BSON, to DAS
data format, JSON.
